CorReg: model-based pretreatment for regression with correlated variables. Application in steel industry

### 2014-04-01 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@476 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

	  In this work, we decide to distinguish the response variable from the other endogenous variables (that are on the left of a regression). Thus we don't have a system of regressions but one regression on our response variable and a system of subregressions (without the response variable). And we consider correlations between the explicative covariates of the main regression, not between the residuals.
	  The structure is supposed to be the source of the correlations and allows us to define a reduced set of independent covariates. Thus we reduce dimension and correlations in the same time. The structure justifies the eviction of the redundant covariates without significant information loss. It can be seen as a pretreatment on the dataset based on the hypothesis of a strong structure between the covariates (i.e. : small $\varepsilon_X$).

	We can use any variable selection method on the reduced dataset with improved efficiency (reduced variance) due to dimension reduction and correlation suppression. So we obtain two kinds of zeros in our first model : coerced zeros due to correlations (redundant information) and estimated ones with classical variable selection methods applied on remaining variables. This two kinds of zero won't be interpreted in the same way and thus consistency issues don't mean interpretation issues any more. So we dodge the drawbacks of both grouping effect and variable selection.

But to work, we need an explicit structure between the covariates. SEM are often used in social sciences and economy where a structure is supposed "by hand" but here we want to be able to find a structure without any a priori (possibility to include some known structure remains). Graphical LASSO \cite{friedman2008sparse} offers a method to obtain a structure based on the precision matrix (inverse of the variance-covariance matrix). It consists in a selection in the precision matrix, setting some covariances to zero. But the resulting matrix is symmetric and we need an oriented graph for our SEM. So we developped an MCMC algorithm to find it (R package CorReg on CRAN). However, Graphical LASSO can be used in the initialization step of our MCMC. This structure is based on a generative model to be able to compare likelihood-based criterion in the MCMC.
 	\\

 	%plan
 	This paper will first present the reduced model and its properties before describing in Section 3 the algorithm used to find the structure.
 	We will then look at some numerical results on simulated (Section \ref{sectionsimul}) and real industrial datasets (Section \ref{sectionrealcase}) before concluding and giving some perspectives in the last part.

>>>>

	  In this work, we decide to distinguish the response variable from the other endogenous variables (that are on the left of a regression). Thus we don't have a system of regressions but one regression on our response variable and a system of subregressions (without the response variable). And we consider correlations between the explicative covariates of the main regression, not between the residuals.
	  The structure is supposed to be the source of the correlations and allows us to define a marginal regression model based on a reduced set of independent covariates without significant information loss. It can be seen as a pretreatment on the dataset because other regression methods can the be used on this reduced and correlation-free set covariates. So we may obtain two kinds of zeros in our first model : coerced zeros due to correlations (redundant information) and estimated ones with classical variable selection methods applied on remaining variables. This two kinds of zero won't be interpreted in the same way and thus consistency issues don't mean interpretation issues any more. So we dodge the drawbacks of both grouping effect and variable selection.

SEM are often used in social sciences and economy where a structure is supposed "by hand" but here we want to find it automatically. Graphical LASSO \cite{friedman2008sparse} offers a method to obtain a structure based on the precision matrix (inverse of the variance-covariance matrix). It consists in a selection in the precision matrix, setting some covariances to zero. But the resulting matrix is symmetric and we need an oriented graph for our SEM. So we developped an MCMC algorithm to find it (R package CorReg on CRAN). However, Graphical LASSO can be used in the initialization step of our MCMC. The structure is based on a full generative model to be able to compare likelihood-based criterion in the MCMC.
 	\\

 	%plan
 	This paper will first present the marginal regression model and its properties before describing in Section 3 the random walk used to find the structure.
 	We will then look at some numerical results on simulated (Section \ref{sectionsimul}) and real industrial datasets (Section \ref{sectionrealcase}) before concluding and giving some perspectives in the last part.
